---
title: 'Space Matters: User Ratings and the Size of Airbnb Listings'
author: "Team 6"
date: "`r Sys.Date()`"
output:
  html_document:
    latex_engine: xelatex
  pdf_document: default
---

```{r setup library, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Loading in packages
library(tinytex)
library(tidyverse)
library(rmarkdown)
library(tidyr)
library(knitr)
library(broom)
library(corrr)
library(svglite)
library(kableExtra)
```

``` {r setup tables, include=FALSE}
# loading the dataset
listings <- read_csv('../../gen/temp/listings_cleaned.csv')

# defining the amount of observations
num_observations <- nrow(listings)

# defining linear models
Reg_Control <- lm(review_scores_rating ~ avg_price + host_response_rate + host_identity_verified + experience_of_hosts_in_years + in_city_center, listings)
Reg_Full <- lm(review_scores_rating ~ bedrooms_per_person + avg_price + host_response_rate + host_identity_verified + experience_of_hosts_in_years + in_city_center, listings)

# Defining table
tab_01 = data.frame(
    Variable = c("Review Score", "Bedrooms per Person", "Average Price per Night", "Host Response Rate", "Host Verified", "Host Experience (Years)", "Location: City Centre"),
    Mean = c(mean(listings$review_scores_rating), mean(listings$bedrooms_per_person), mean(listings$avg_price), mean(listings$host_response_rate), mean(listings$host_identity_verified), mean(listings$experience_of_hosts_in_years), mean(listings$in_city_center)), 
    SD = c(sd(listings$review_scores_rating), sd(listings$bedrooms_per_person), sd(listings$avg_price), sd(listings$host_response_rate), sd(listings$host_identity_verified), sd(listings$experience_of_hosts_in_years), sd(listings$in_city_center)),
    Min = c(min(listings$review_scores_rating), min(listings$bedrooms_per_person), min(listings$avg_price), min(listings$host_response_rate), min(listings$host_identity_verified), min(listings$experience_of_hosts_in_years), min(listings$in_city_center)),
    Max = c(max(listings$review_scores_rating), max(listings$bedrooms_per_person), max(listings$avg_price), max(listings$host_response_rate), max(listings$host_identity_verified), max(listings$experience_of_hosts_in_years), max(listings$in_city_center))
)

# Defining the correlation table
cor_tab = listings %>% 
  select(review_scores_rating, bedrooms_per_person, avg_price, host_response_rate, host_identity_verified, experience_of_hosts_in_years, in_city_center) %>% 
  correlate() %>% 
  shave(upper = TRUE) %>% 
  fashion(decimals = 2, na_print = "—")
```

\newpage
# Introduction & Model Specification
This project will look at the following research question:

\newline

*"Does the number of bedrooms per person have a significant effect on accommodation ratings?"*

\newline

For further details on motivation, please refer to our GitHub page or the README file.

\newline

## Model Specification
To get an answer to our research question, we use linear models in a linear regression analysis. The models are as follows:

\newline
\newline

#### Control model
Review Score = β0 + β1 * Average Price per Night + β2 * Host Response Rate + β3 * Host Verified + β4 * Host Experience (Years) + β5 * Location: City Centre + ε

\newline

\newline

#### Full model
Review Score = β0 + β1 * Bedrooms per Person + β2 * Average Price per Night + β3 * Host Response Rate + β4 * Host Verified + β5 * Host Experience (Years) + β6 * Location: City Centre + ε

\newline

# Descriptive Statistics

The following tables show the descriptive statistics of our models. 

```{r descriptive tables, echo=FALSE}
kable(
  tab_01,
  col.names = c("Variable", "Mean", "SD", "Min", "Max"),
  digits = 3,
  caption = sprintf("Means, Standard Deviations, Minima, and Maxima of all variables used in the full regression analysis. n = %d ", num_observations)
) %>%
  kable_material(c("striped", "hover"))
```

```{r Correlation Table, echo=FALSE}
kable(
  cor_tab,
  caption = "Correlations between variables"
) %>%
  kable_material(c("striped", "hover"))
```

\newline
# Results
These tables show the results of our linear models.

\newline

```{r models, echo=FALSE}
Reg_Control %>%
  tidy() %>%
  mutate(
    p.value = scales::pvalue(p.value),
    term = c("(Intercept)", "Average Price per Night", "Host Response Rate", "Host Verified", "Host Experience (Years)", "Location: City Centre")
  ) %>%
  kable(
    caption = "Coefficient-Level Estimates for the Control Model",
    col.names = c("Predictor", "B", "SE", "t", "p"),
    digits = c(0, 3, 3, 2, 3),
    align = c("l", "r", "r", "r", "r")
  ) %>%
  kable_material(c("striped", "hover"))
```

```{r, echo=FALSE}
Reg_Full %>%
  tidy() %>%
  mutate(
    p.value = scales::pvalue(p.value),
    term = c("(Intercept)", "Beds per Person", "Average Price per Night", "Host Response Rate", "Host Verified", "Host Experience (Years)", "Location: City Centre")
  ) %>%
  kable(
    caption = "Coefficient-Level Estimates for the Full Model",
    col.names = c("Predictor", "B", "SE", "t", "p"),
    digits = c(0, 3, 3, 2, 3),
    align = c("l", "r", "r", "r", "r")
  ) %>%
  kable_material(c("striped", "hover"))
```

\newpage

# Plotting Review Scores and Bedrooms per Person

```{r Plots, echo=FALSE, message=FALSE}
ggplot(data = listings, aes(x = bedrooms_per_person, y = review_scores_rating)) +
  geom_point() + # Add points for the scatter plot
  geom_smooth(method = "lm", se = FALSE) + # Add a linear regression line (change method as needed)
  labs(x = "Bedrooms per Person", y = "Review Score") + # Add axis labels
  ggtitle("Scatter Plot of Bedrooms per Person vs. Review Score") # Add a title

```
